The \dealii{} Library, Version 8.5

### 2017-03-19 8.5/paper.tex
Add one name.

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
Rajat  Arora,
Mauro  Bardelloni,
Conrad  Clevenger,
Sam  Cox,
Juliane  Dannberg,
Ren{\'e}  Gassm{\"o}ller,
Joscha  Gedicke,
Sebastian  Gonzalez-Pintor,
Ryan  Grove,
Michael  Harmon,
Daniel  Jodlbauer,
Guido  Kanschat,
Justin  Kauffman,
Paul  Kuberry,
Dustin  Kumor,
Konstantin  Ladutenko,
Andrew  McBride,
Mathias  Mentler,
Andrea  Mola,
Dragan  Nikolic,
Vaibhav  Palkar,
Spencer  Patty,
Jonathan  Perry-Houts,
Giuseppe  Pitton,
Ce  Qin,
Jonathan  Robey,
Mayank  Sabharwal,
Ali  Samii,
Alberto  Sartori,
Daniel  Shapero,
Martin  Steigemann,
Jihuan  Tian,
Jaeryun  Yim,
Toby  Young,
Zhao  Liang.

>>>>

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
Rajat  Arora,
Mauro  Bardelloni,
Conrad  Clevenger,
Sam  Cox,
Juliane  Dannberg,
Niklas Fehn,
Ren{\'e}  Gassm{\"o}ller,
Joscha  Gedicke,
Sebastian  Gonzalez-Pintor,
Ryan  Grove,
Michael  Harmon,
Daniel  Jodlbauer,
Guido  Kanschat,
Justin  Kauffman,
Paul  Kuberry,
Dustin  Kumor,
Konstantin  Ladutenko,
Andrew  McBride,
Mathias  Mentler,
Andrea  Mola,
Dragan  Nikolic,
Vaibhav  Palkar,
Spencer  Patty,
Jonathan  Perry-Houts,
Giuseppe  Pitton,
Ce  Qin,
Jonathan  Robey,
Mayank  Sabharwal,
Ali  Samii,
Alberto  Sartori,
Daniel  Shapero,
Martin  Steigemann,
Jihuan  Tian,
Jaeryun  Yim,
Toby  Young,
Zhao  Liang.
